Molecular dynamics simulation of synchronization in driven particles

### 2020-11-03 manuscript/manuscript_ajp_2020.tex
added symbols for talk

Particles are subject an external time-dependent driving force
$\vec{F}_{D}(t)$
applied parallel to the y-direction.
We model this force as
\begin{equation}
\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y},
\end{equation}
with modifiable parameters including
a constant component $F_{DC}$,
and a time dependent component with amplitude $F_{AC}$
and frequency $\omega = 2 \pi f$.
The frequency is scaled in time units,
where [finish].
 We demonstrate how a single particle (Sec.~\ref{sec:one})
 and many particles
 move (Sec.~\ref{sec:twenty})
 in response to this applied force in a variety of light fields.
 In Sec.~\ref{sec:kink} we set $F_{DC}$
 to zero and track the motion
 of a high density area of a particle chain
 (i.e. kink dynamics).
 %The driving force does add energy into the system, and some of it is lost.

@@

We place a single particle in a periodic light field is
\begin{equation}
  V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
\end{equation}
where $N_p=20$ are the number of troughs in the landscape,
and $V_{0x}=2$ and $V_{0x}=2$.
This is illustrated in Fig.~\ref{fig:1}(a) where
the red regions show local maxima and the blue local minima.
We apply an external applied force, 
with 
a constant $F_{AC}$ with frequency $\omega$ then slowly increase $F_{DC}$.
The particle hops between troughs in the energy landscape
when the superposition of $F_{AC}$ and $F_{DC}$ is large enough
to overcome the barrier height.
By modifying $F_{DC}$ we 
achieve a variety of oscillation modes.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\bar{v}_{y}$
over a range of driving forces $F_{DC}$.
We illustrate mode-locking in 
the velocity-force plot in Fig.~\ref{fig:1}(b).
Here $\bar{v}_{y}$ is increasing in non-uniform steps.
Our simulations reproduce 
Juniper {\it et al.} \cite{juniper2015}
which demonstrated
mode locking in driven colloids on a
optical periodic landscape.

>>>>

Particles are subject an external time-dependent driving force
$\vec{F}_{D}(t)$
applied parallel to the y-direction.
We model this force as
\begin{equation}
\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(\omega t)] \hat{y},
\end{equation}

\begin{equation}
\vec{F}_{D}(t) = [F_{DC} + F_{AC} \sin(2 \pi f t)] \hat{y} 
\end{equation}

\begin{equation}
F_{DC} = 0.01
\end{equation}

\begin{equation}
F_{AC} = 0.2 
\end{equation}

\begin{equation}
f = 0.01 
\end{equation}

\begin{equation}
\bar{v}_y = n \lambda f
\end{equation}

\begin{equation}
\bar{v}_y = \lambda f
\end{equation}

\begin{equation}
\lambda = S_Y / 20
\end{equation}

\begin{equation}
F_{p} = 0.1
\end{equation}

with modifiable parameters including
a constant component $F_{DC}$,
and a time dependent component with amplitude $F_{AC}$
and frequency $\omega = 2 \pi f$.
The frequency is scaled in time units,
where [finish].
 We demonstrate how a single particle (Sec.~\ref{sec:one})
 and many particles
 move (Sec.~\ref{sec:twenty})
 in response to this applied force in a variety of light fields.
 In Sec.~\ref{sec:kink} we set $F_{DC}$
 to zero and track the motion
 of a high density area of a particle chain
 (i.e. kink dynamics).
 %The driving force does add energy into the system, and some of it is lost.

@@

We place a single particle in a periodic light field is
\begin{equation}
  V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
\end{equation}
where $N_p=20$ are the number of troughs in the landscape,
and $V_{0x}=2$ and $V_{0x}=2$.
This is illustrated in Fig.~\ref{fig:1}(a) where
the red regions show local maxima and the blue local minima.
We apply an external applied force, 
with 
a constant $F_{AC}$ with frequency $\omega$ then slowly increase $F_{DC}$.
The particle hops between troughs in the energy landscape
when the superposition of $F_{AC}$ and $F_{DC}$ is large enough
to overcome the barrier height.
By modifying $F_{DC}$ we 
achieve a variety of oscillation modes.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\bar{v}_{y}$
over a range of driving forces $F_{DC}$.
We illustrate mode-locking in 
the velocity-force plot in Fig.~\ref{fig:1}(b).
Here $\bar{v}_{y}$ is increasing in non-uniform steps.
Our simulations reproduce results presented in 
Juniper {\it et al.} \cite{juniper2015}
which demonstrated
mode locking in
experiments of 
driven colloids on a
optical periodic landscape.
